Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-18 Markdown Documents/Manuscript.Rmd
Started Cross validation section

# 2. Methods
```{r include=FALSE, cache=TRUE}
library(tidyverse)
library(lme4)
library(rstanarm)
library(rstan)
library(zoo)
library(formattable)
load("~/SmokeProject/ModelObjects/feefit.rda")
load("~/SmokeProject/ModelObjects/residuals.rda")
```
## 2.1. Data Collection

@@

summaryFinancialLoss<-summaryFinancialLoss[,c(6,4,5)]
summaryFinancialLoss$IncomeDif<-currency(summaryFinancialLoss$IncomeDif)
names(summaryFinancialLoss)<-(c("National Park","Income Loss Estimate (1980-2018)", "Percent Income Loss (1980-2018)"))
summaryFinancialLoss$`Percent Income Loss (1980-2018)`<-paste0(summaryFinancialLoss$`Percent Income Loss (1980-2018)`,'%')
formattable::formattable(summaryFinancialLoss)
```
## 3.3. Model Validation

>>>>

# 2. Methods
```{r include=FALSE, cache=TRUE}
library(tidyverse)
library(lme4)
library(rstanarm)
library(rstan)
library(zoo)
library(formattable)
load("~/SmokeProject/ModelObjects/feefit.rda")
load("~/SmokeProject/ModelObjects/residuals.rda")
load("~/SmokeProject/ModelObjects/CVResidualMod.rds")
```
## 2.1. Data Collection

@@

summaryFinancialLoss<-summaryFinancialLoss[,c(6,4,5)]
summaryFinancialLoss$IncomeDif<-currency(summaryFinancialLoss$IncomeDif)
names(summaryFinancialLoss)<-(c("National Park","Income Loss Estimate (1980-2018)", "Percent Income Loss (1980-2018)"))
summaryFinancialLoss$`Percent Income Loss (1980-2018)`<-paste0(summaryFinancialLoss$`Percent Income Loss (1980-2018)`,'%')
formattable::formattable(summaryFinancialLoss)
```
## 3.3. Model Validation
To assess the validity of our model, we used a k-fold cross validation technique.
